\section*{附录1：短句测试库}{Appendix 1: Short Sentences Corpus}
 
Will the danger increase or decrease?
 
Readiness exercises  are almost continuous. 

Each could be the real thing. 

These men are not callous. 

That's the law. 

He makes the momentous decision. 

In a word, plenty.

The answer is a cryptographic secret. 

Their heads were in the air sniffing. 

They were chasing a rain cloud. 

Sometimes it was to skirt a gully. 

They ran for three hours. 

They were studying the ground. 

Part of it is, of course. 

Such stretches have an inhuman moonlike quality. 

No one came. 

The white men died. 

And countless others like them have died. 

The aborigine is not deceived.


Damned right , he said. 

He was right. 

The landscape kept repeating itself. 

No one patted the dog. 

It was not a pet. 

It was a worker. 

The man was leaning against the rock. 

His legs were narrow and very long. 

A cigarette would taste particularly good. 

I really didn't know what he meant. 

It was a nice day, granted. 

It is a splendid structure. 

It is a great spectacle. 

Yes, the Maestro assented. 

What did he do for relaxation?

You might have failed. 

The Frenchman was astonished. 

Tobacco Road is dead. 

Long live Tobacco Road. 

In 1950 it had become 47.1\% urban. 

The list is, obviously, endless. 

But these sources have not been tapped. 

It bewilders and befuddles him. 

The concept remains subjective. 

The system works as an impersonal mechanism. 

But the metamorphosis must come first. 

Events occur without apparent reason. 

Each performance may be different. 

Then the choreographer must arbitrate. 

One wonders about its applicability to people. 

The range of our voice ignores distance. 


Perhaps things were even worse then. 

A meteor could fall on San Francisco. 

Yet we no longer feel uneasy. 


He was waiting. 

They find deep pessimism in them. 

Nevertheless I was curious. 

Beckett's appearance is rough-hewn Irish. 

The confusion is not my invention. 

I am not a philosopher. 

It has held them at bay. 

And why not?

Beckett's own work is an example. 

The form and the chaos remain separate. 

Isn't all art ambiguous?

Not this. 

This is clear. 

With classical art, all is settled. 

But it is different at Chartres. 

Yes. 

That is the play. 

I have no religious feeling. 

Once I had a religious emotion. 

It was at my first Communion. 

No more. 

My mother was deeply religious. 

So was my brother. 

My father had none. 

But there is also compassion. 

That is reserved for the squares. 

It is sacred. 

They are non-conformists on principle. 

There is nothing holy in wedlock. 

Boredom is death. 

What one actually remembers is its greenness. 

Another had ended before it began. 

Time in the sum is nothing. 

It was mother who planted the verbenas. 

He collapses, and dies. 

His rage assumes a religious form.

The image of God has simply disappeared. 

The expression has become quite a cliche.

How do we define it ?

Circumstances alter cases. 

Who is involved willy nilly?

Complicity is an embarrassing word. 

Who is the owner?

Pay him !

But can one, really?

But that was a long time ago.

The New England conscience became desensitized.


\end{document}

